Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-24 papers/BON_VHDL/paper.tex
minor correction
text correction

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility} and software \emph{contracting}. Let us define 
these principles precisely and point out why the principles are 
important in VHDL-AMS simulation.

@@

\subsection{Contracting}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre(post) condition trought input(output) 
parameters and theirs constraints. Furthermore any subtype(subnature) 
represents restricted set of values from a base type(nature). 
The condition that determines which values are in the subtype(subnature)  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformations are shown 
by the example below:
\input{bitbon}
Therefore as an notition based on contract design, and as  methodology of 
best modelling practices, BON is the obvious choice for the our simulator.
Throughout this paper we will try to make this more clearly.

>>>>

\section{Choice of BON as the modeling tool}
%Brief description and motivation.
The Business Object Notation (BON) is an analysis and design notation 
for object-oriented systems  which emphasizes \emph{seamlessness}, 
\emph{reversibility},software \emph{contracting} and \emph{refinement}. 
Let us define these principles precisely and point out why the principles 
are important in VHDL-AMS simulation.

@@

\subsection{Contracting and Refinement}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre(post) condition trought input(output) 
parameters and theirs constraints. Furthermore any subtype(subnature) 
represents restricted set of values from a base type(nature). 
The condition that determines which values are in the subtype(subnature)  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformations are shown 
by the example below:
\input{bitbon}
The current IEEE standard VHDL-AMS language reference manual 
tries to define VHDL-AMS as well as possible in a descriptive way, 
explaining the semantics in English. As we have shown in example above,
BON has an easily-readable, English-based textual notation.\\
Therefore as an notition based on contract design, and as  methodology of 
best modelling practices, BON is the obvious choice for the our simulator.
Throughout this paper we will try to make this more clearly.
